Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-05-01 paper/paper7/paper7.tex
introduction

The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts. All in all, this lead to 246 constraints on six vocabularies. 
We let the experts classify the constraints according to the severity if they are violated. Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions), 
over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible 
%(e.g., constraints on network topologies)
(e.g., constraints on graph-based structures}).

@@

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.

@@

We identified and published by today 82 types of constraints\footnote{The first appendix of this paper, in which we explain each requirement/constraint type in detail, is available at: \url{http://arxiv.org/abs/1501.03933} \cite{BoschNolleAcarEckert2015}}
that are required by various stakeholders for data applications.
In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
 of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.

>>>>

The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts. All in all, this lead to 246 constraints  of 53 different types on six vocabularies. \tb{in total 82 constraint types}
We let the experts classify the constraints according to the severity if they are violated. Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions), 
over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible 
%(e.g., constraints on network topologies)
(e.g., constraints on graph-based structures}).

@@

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
The remainder of the paper is structured as follows.

@@

We identified and published by today 82 types of constraints\footnote{The first appendix of this paper, in which we explain each requirement/constraint type in detail, is available at: \url{http://arxiv.org/abs/1501.03933} \cite{BoschNolleAcarEckert2015}}
that are required by various stakeholders for data applications.
In close collaboration with several \emph{SBE} domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
 of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
